---
title: "Data Analysis"
author: "Power Ninja Data Turtles"
date: "12.03.2019"
output: github_document
---

### Load data and packages

```{r load-data-and-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(infer)
library(broom)

fight_songs <- read_csv("/cloud/project/data/fight-songs.csv")
fight_songs <- fight_songs %>%
  select(-X21)
```

### Research Question 1

Our first research question is:

>"How does the tempo and duration of a college football team's fight song predict the content of the song, specifically the number of clichés/tropes?

Before we delve deeper into our analysis, let's first take a look at the distributions of our two explanatory variables, `bpm` and `sec_duration`.

Starting with `bpm`, which is a measure of a fight song's tempo, we will create a histogram and find the relevant summary statistics:

```{r histogram-bpm}
ggplot(fight_songs, mapping = aes(x = bpm)) +
  geom_histogram(binwidth = 10) +
  labs(title = "Tempo of College Fight Songs",
       x = "Beats per Minute (bpm)",
       y = "Number of Songs")
```

Let’s also calculate the summary statistics for this distribution. Specifically, we will use the median as a measure of center and the interquartile range as a measure of spread (due to the bimodal nature of the distribution). In addition, we will find the upper and lower quartiles (Q3 and Q1, respectively), and the maximum and minimum values:

```{r calc-summary-stats-bpm}
fight_songs %>%
  summarise(min = min(bpm),
            Q1 = quantile(bpm, 0.25),
            median = median(bpm),
            Q3 = quantile(bpm, 0.75),
            max = max(bpm),
            IQR = IQR(bpm))
```

Based on the histogram, it is clear that the shape of the data is clearly bimodal, with two distinct peaks occurring around 70 bpm and around 150 bpm, with a split in the data at around 100 bpm. There are more songs that are clustered around the higher bpm mode. The center (median) occurs at 140 bpm, and the spread (IQR) is 61 bpm, indicating that there is a moderate amount of variability in tempos. There are no outliers in this distribution. Due to the bimodal result, it seems like there is a natural grouping between “slow” songs and “fast” songs, so we will use the `mutate()` function to add a new variable, `tempo`, which is "slow" if a song's `bpm` is less than or equal to 100 bpm and "fast" if a song's tempo is greater than 100 bpm.

```{r mutate-tempo}
fight_songs <- fight_songs %>%
  mutate(tempo = case_when(
    bpm <= 100 ~ "slow",
    bpm > 100 ~ "fast"
  ))
```

Now, let's start exploring our second explanatory variable, `sec_duration`, which is the duration of a song in seconds. In order to do this, we will create a histogram of the distribution and find the relevant summary statistics:

```{r histogram-summary-stats-sec_duration}
ggplot(fight_songs, mapping = aes(x = sec_duration)) +
  geom_histogram(binwidth = 20) +
  labs(title = "Duration of College Fight Songs",
       x = "Duration (sec)",
       y = "Number of Songs")

fight_songs %>%
  summarise(min = min(sec_duration),
            Q1 = quantile(sec_duration, 0.25),
            median = median(sec_duration),
            Q3 = quantile(sec_duration, 0.75),
            max = max(sec_duration),
            IQR = IQR(sec_duration))
```

Based on the histogram, we can see that the distribution of fight song durations is roughly symmetric (slightly skewed to the right) and unimodal, with a peak at around 70. There are some outliers on the higher end of the spectrum (`sec_duration` > 125.5), indicating that these songs are significantly longer than the others. The center of the distribution occurs at around 67 seconds, and the IQR of the distribution is 27 seconds, which is relatively narrow, indicating that fight songs do not have dramatically different lengths. Like we did with `bpm`, let's add a new variable, `length`, which is "short" if a song is less than or equal to the median of 67 seconds and "long" if a song is greater than the median of 67 seconds.

```{r mutate-length}
fight_songs <- fight_songs %>%
  mutate(length = case_when(
    sec_duration <= 67 ~ "short",
    sec_duration > 67 ~ "long"
  ))
```

Now that we have a better understanding of our two explanatory variables, we want to add a new variable, `classify`, which combines `bpm` and `sec_duration` by labeling each song with one of four classifications: "slow and short", "slow and long", "fast and short", and "fast and long":

```{r mutate-classify}
fight_songs <- fight_songs %>%
  mutate(classify = case_when(
    tempo == "slow" & length == "short" ~ "slow and short",
    tempo == "slow" & length == "long" ~ "slow and long",
    tempo == "fast" & length == "short" ~ "fast and short",
    tempo == "fast" & length == "long" ~ "fast and long",
  ))

fight_songs %>%
  count(classify)
```

Based on the output displayed in the tibble above, 23 songs are categorized as "fast and long", 25 songs are categorized as "fast and short", 9 songs are categorized as "slow and long", and 8 songs are categorized as "slow and short".

Using these classifications, let's visualize the groups and fill in each observation with the number of tropes associated with that particular observation. We choose to use `geom_hline()` and `geom_vline()` to add horizontal and vertical reference lines to the jittered plot (`geom_jitter()` adds a small amount of random variation to the location of each point). We also choose to use `scale_color_gradientn()` to create a rainbow-colored gradient scale.

```{r visualize-classify}
ggplot(fight_songs, mapping = aes(x = sec_duration, y = bpm)) +
  geom_jitter(aes(color = trope_count)) + 
  geom_hline(yintercept = 100, linetype = "dashed", color = "orange") +
  geom_vline(xintercept = 67, linetype = "dashed", color = "orange") +
  theme_minimal() +
  labs(title = "Classification of College Fight Songs", 
       subtitle = "By tempo and duration",
       x = "Duration (sec)",
       y = "Tempo (bpm)",
       color = "Number of Tropes") +
  scale_color_gradientn(colors = rainbow(5))
```

The upper left-hand region of the plot represents songs that are "fast and short" while the lower left-hand region represents songs that are "slow and short." The upper right-hand region of the plot represents songs that are "fast and long", and the lower right-hand region represents songs that are "slow and long".

Finally, let's get an understanding of our response variable, `trope_count`, which is a measure of the number of clichés/tropes in a given fight song. We will also use a histogram and summary statistics for this univariate analysis:

```{r histogram-summary-stats-trope_count}
ggplot(fight_songs, mapping = aes(x = trope_count)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Number of Clichés in College Fight Songs",
       x = "Number of Clichés",
       y = "Number of Songs")

fight_songs %>%
  summarise(min = min(trope_count),
            Q1 = quantile(trope_count, 0.25),
            median = median(trope_count),
            Q3 = quantile(trope_count, 0.75),
            max = max(trope_count),
            IQR = IQR(trope_count),
            sd = sd(trope_count))
```

Based on the histogram and summary statistics, we can see that the distribution for number of tropes is unimodal with a peak at around 4 and skewed slightly to the left. There is 1 outlier at the maximum value of our distribution (8 tropes). The center of the distribution, described by the median, is 4 tropes, and the IQR of 2 indicates that there is not a large amount of variability in the number of tropes for college fight songs.

Now, let's return to our research question by examining whether the amount of clichés varies based on a song's classification. First, we will create violin plots for the distribution of the number of tropes for each classification and add jitter. Using jittered points allows us to manage the effects of overplotting when working with smaller datasets. We were inspired to use this type of plot after conferencing with Dr. Eric Monson who delivered the "Tips for Effective Data Visualization" presentation earlier this semester.

```{r boxplots-summary-statsnumber_tropes}
ggplot(fight_songs, mapping = aes(x = classify, y = trope_count)) +
  geom_violin(draw_quantiles = c(0.25, 0.50, 0.75)) +
  geom_jitter() +
  labs(title = "Number of Clichés",
       subtitle = "By Song Classification",
       x = "Song Classification",
       y = "Number of Clichés")

fight_songs %>%
  group_by(classify) %>%
  summarize(median = median(trope_count), IQR = IQR(trope_count), sd = sd(trope_count))
```

Not surprisingly, all of the distributions, except for "slow and long", are centered at 4 tropes, which is the median number of tropes for all songs in the dataset. However, there is one category, "slow and long," which has a median of 5. We would like to check whether this median is statistically significant or not. To do this, we will conduct a hypothesis test for the median number of tropes for songs that are considered "slow and long". Our null hypothesis is that the true median number of tropes for "slow and long" songs is 4, H0: median("slow and long") = 4. Our alternative hypothesis is that the true median number of tropes is different than 4, Ha: median("slow and long") ≠ 4. We will use a significance (alpha) level of 0.05. Let's create and visualize the null distribution and calculate the associated p-value:

```{r hypothesis-test-slow-and-long}
obs_median <- 5 # From summary statistics in previous code chunk

slow_long <- fight_songs %>%
  filter(classify == "slow and long")

set.seed(11101962)
null_slow_long <- slow_long %>%
  specify(response = trope_count) %>%
  hypothesize(null = "point", med = 4) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median")

get_p_value(null_slow_long, obs_stat = obs_median, direction = "two_sided")

visualise(null_slow_long) + 
  labs(title = "Null Distribution for Median Number of Tropes",
       subtitle = "For Slow and Long Fight Songs",
       x = "Sample Median Number of Tropes",
       y = "Count") +
  shade_p_value(obs_stat = obs_median, direction = "two_sided")
```

Based on our p-value of 0.038, which is less than 0.05 (significance level), we reject the null hypothesis in favor of the alternative hypothesis; in other words, there is sufficient evidence that the true median number of tropes is different than 4. Thus, the data provide convincing evidence that the median number of tropes for songs that are slow and long is different than the population median of 4. However, our sample size is very small (9 observations), so we must be wary of our results and acknowledge the limitations of our conclusions.

We can also see from the visualization "Number of Clichés" that the spread for "slow and short" songs is much smaller compared to all other song classifications. We will test whether the standard deviation for "slow and short" songs is significantly different from the population standard deviation of 1.675. 

The null hypothesis is that the true standard deviation in the number of tropes for "slow and short" songs is 1.675, H0: sigma = 1.675. 

The alternative hypothesis is that the true standard deviation in the number of tropes for "slow and short" songs is less than 1.675, Ha: sigma < 1.675. We will use a significance level of 0.05.

```{r hypothesis-test-slow-and-short}
obs_sd <- 1.13 # From summary statistics in previous code chunk

slow_short <- fight_songs %>%
  filter(classify == "slow and short")

set.seed(11101962)
null_slow_short <- slow_short %>%
  specify(response = trope_count) %>%
  hypothesize(null = "point", sigma = 1.675) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "sd")

get_p_value(null_slow_short, obs_stat = obs_sd, direction = "left")

visualise(null_slow_short) + 
  labs(title = "Null Distribution for Standard Deviation of Tropes",
       subtitle = "For Slow and Short Fight Songs",
       x = "Sample Standard Deviation of Tropes",
       y = "Count") +
  shade_p_value(obs_sd, direction = "left")
```

Based on the p-value of 0.685, which is greater than our alpha level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis; in other words, the data do not provide convincing evidence that the true standard deviation for slow and short songs is less than the population standard deviation of 1.675.

Now, let's find the full linear model that predicts number of tropes (`trope_count`) from tempo (`bpm`) and duration (`sec_duration`):

```{r model_full_trope_count}
(m_full <- lm(trope_count ~ bpm + sec_duration, data = fight_songs)) %>%
  tidy() %>%
  select(term, estimate)

glance(m_full)$AIC
glance(m_full)$r.squared
```

Based on the output, the full linear model is `trope_count-hat` = 4.58 - 0.00757 * `bpm` + 0.000208 * `sec_duration`. The R-squared value is `r glance(m_full)$r.squared`, which means that approximately `r glance(m_full)$r.squared *100`% of the variability in trope counts can be explained by the linear model that predicts trope count from a song's tempo and duration. Given this R-squared value, our model is very weak, since, in general, the closer the R-squared value is to 1 (100% of the variability in trope counts can be explained by the model), the more accurate and useful the final model is. As the model only accounts for a small percent of the variability in trope counts, it is not a great predictor of a fight song's trope count.

The intercept tells us that for a song with 0 bpm which lasts 0 seconds, the expected number of tropes is 4.58. But of course, this is nonsensical, since none of the fight songs we are considering in our analysis last 0 seconds (for that matter, no songs, by definition, last 0 seconds!). The slope coefficient associated with `bpm` tells us that for an increase in 1 bpm, the number of tropes is expected, on average, to decrease by 0.00757, holding all else constant. The slope coefficient associated with `sec_duration` tells us that for an increase in a song's duration by 1 second, the number of tropes is expected, on average, to increase by 0.000208, holding all else constant. 

Now, we will conduct a hypothesis test for the slopes to determine whether the slope coefficients for `bpm` and `sec_duration` are significantly different from 0. We will use a significance level of 0.05. Conducting a hypothesis test for the slopes will help us confirm or deny our research question on whether either tempo or duration are useful predictors of the content of a fight song, as determined by a song's number of tropes.

Let our null hypotheses be that the slope coefficients associated with both variables are 0; H0: beta(`bpm`) = 0 and beta(`sec_duration`) = 0.

Let our alternative hypotheses be that the slope coefficients associated with both variables are significantly different than 0, Ha: beta(`bpm`) ≠ 0 and beta(`sec_duration`) ≠ 0.

```{r hypothesis-test-bpm-slope}
obs_beta_bpm <- tidy(m_full) %>%
  select(estimate) %>% 
  slice(2) %>% 
  pull() 

set.seed(11101962)
null_dist_bpm_slope <- fight_songs %>%
  specify(response = trope_count, explanatory = bpm) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope")

get_p_value(null_dist_bpm_slope, obs_stat = obs_beta_bpm, direction = "two_sided")

visualise(null_dist_bpm_slope) + 
  labs(title = "Null Distribution for Tempo Slope Coefficient",
       subtitle = "In full linear model for trope count",
       x = "Sample bpm Slope Coefficients",
       y = "Count") +
  shade_p_value(obs_beta_bpm, direction = "two_sided")
```

```{r hypothesis-test-sec-duration-slope}
obs_beta_sec_duration <- tidy(m_full) %>% 
  select(estimate) %>% 
  slice(3) %>%
  pull() 

set.seed(11101962)
null_dist_sec_duration_slope <- fight_songs %>%
  specify(response = trope_count, explanatory = sec_duration) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope")

get_p_value(null_dist_sec_duration_slope, obs_stat = obs_beta_sec_duration, direction = "two_sided")

visualise(null_dist_sec_duration_slope) + 
  labs(title = "Null Distribution for Song Duration Slope Coefficient",
       subtitle = "In full linear model for trope count",
       x = "Sample Song Duration Slope Coefficients",
       y = "Count") +
  shade_p_value(obs_beta_sec_duration, direction = "two_sided")
```

The p-values for the slope coefficients of `bpm` and `sec_duration` are 0.238 and 0.978, respectively. Since both p-values are greater than our alpha level of 0.05, we should fail to reject the null hypotheses in favor of the alternative hypotheses. Hence, there appears to be insufficient evidence that the slope coefficients for `bpm` and `sec_duration` are different than 0. 

However, we must must verify that the four conditions for inference for regression are satisfied before finalizing any conclusions: (1) observations should be independent; (2) residuals should be randomly distributed around 0; (3) residuals should be nearly normally distributed, centered at 0; (4) residuals should have constant variance.

First, we can assume that the observations (fight songs) are independent because college fight songs are unique to every team and written by different authors.

Next, we will verify our assumption (confirm independence of observations) by plotting the residuals in the order of data collection:

```{r testing-condition-1}
m_full_aug <- augment(m_full)
ggplot(data = m_full_aug, aes(x = 1:nrow(m_full_aug), y = .resid)) +
  geom_point() +
  labs(title = "Residual Plot by Index",
       subtitle = "In the order of data collection",
       x = "Index",
       y = "Residual")
```

Next, let's examine the normality of residuals:

```{r testing-condition-3}
ggplot(data = m_full_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 1.25) +
  labs(title = "Normality of Residuals",
       x = "Residuals")
```

Finally, we will check the distribution of residuals around 0 and constant variance:

```{r testing-conditions-2-and-4}
ggplot(data = m_full_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, lty = 3, color = "blue") +
  labs(title = "Distribution of Residuals",
       x = "Predicted values, y-hat",
       y = "Residuals")
```

Clearly, condition 4 (constant variance) is violated. Therefore, inference for regression is invalid. This means our conclusion that there is insufficient evidence to suggest the slope coefficients for `bpm` and `sec_duration` are different than 0 is also not credible.

To confirm that there is no better linear model, we will use the `step()` function and backwards selection with AIC as the selection criterion:

```{r backwards_selection_trope_count, results = "hide"}
(m_trope_count <- step(m_full, direction = "backward")) 
```

```{r AIC-m_trope_count}
m_trope_count %>%
  tidy() %>%
  select(term, estimate)
glance(m_trope_count)$AIC
```

Since backwards selection removed both `bpm` and `sec_duration` from our model, we should conclude that these two variables are not valid predictors for the number of tropes in a college fight song.

However, we must consider one last element before concluding that `bpm` and `sec_duration` are poor predictors of `trope_count`: whether the requirements for linear regression are satisfied. Amongst other things, a linear model mandates a continuous numerical response variable! But, it is clear that `trope_count` does not fulfill this criterion since it is a counting (discrete) numerical response variable. Thus, our final conclusions are as follows: this method of analysis involving linear regression is invalid and there is no guarantee that the explanatory variables are poor predictors of the response variable.

Circling back to our research question, it appears as though we have insufficient evidence to describe the correlation (if any) between our two explanatory variables, `bpm` and `sec_duration`, and the trope count for a given fight song. The only evidence that we have is that "slow and long" fight songs have a different median number of tropes than other fight songs.

### Research Question 2

Our second research question is:

> "How do characteristics of the fight songs of college football teams correspond to their respective historical levels of success (rankings)?

Before we delve deeper into our analysis, let's first take a look at the distributions of our four explanatory variables, `victory_win_won`, `opponents`, `nonsense`, and `rah`, and our response variable, `rank`.

We will begin our analysis with `victory_win_won`, which designates whether a fight song says "victory", "win", or "won", by creating a bar graph:

```{r visualize_victory_win_won}
ggplot(fight_songs, mapping = aes(x = victory_win_won)) +
  geom_bar() +
  labs(title = "Distribution of Whether Fight Songs Include 'victory', 'win', or 'won'",
       x = "Whether Fight Song Includes 'victory', 'win', or 'won'",
       y = "Number of College Football Teams")
```

Next, we will look at `opponents`, which designates whether a song mentions an opponent, by creating a bar graph:

```{r visualize_opponents}
ggplot(fight_songs, mapping = aes(x = opponents)) +
  geom_bar() +
  labs(title = "Distribution of Whether Fight Songs Include Opponents",
       x = "Whether Fight Song Includes Opponents",
       y = "Number of College Football Teams")
```

Now, we will explore `nonsense`, which designates whether a song includes any nonsense words/phrases, by creating a bar graph:

```{r visualize_nonsense}
ggplot(fight_songs, mapping = aes(x = nonsense)) +
  geom_bar() +
  labs(title = "Distribution of Whether Fight Songs Include Nonsense",
       x = "Whether Fight Song Includes Nonsense Words",
       y = "Number of College Football Teams")
```

Then, we will examine `rah`, which designates whether a fight song says the word "rah", by creating a bar graph:

```{r visualize_rah}
ggplot(fight_songs, mapping = aes(x = rah)) +
  geom_bar() +
  labs(title = "Distribution of Whether Fight Songs Include 'rah'",
       x = "Whether Fight Song Includes 'rah'",
       y = "Number of College Football Teams")
```

Finally, we will look at `rank`, which corresponds to the team's AP college football ranking. We will create a histogram and calculate the appropriate summary statistics:

```{r visualize_rank}
ggplot(fight_songs, mapping = aes(x = rank)) +
  geom_histogram(bins = 10) +
  labs(title = "Distribution of College Football Rankings",
       x = "Rank",
       y = "Number of College Football Teams")
```

In calculating the summary statistics for `rank`, we will use the median as a measure of center and the interquartile range as a measure of spread (due to the skewed nature of the distribution). In addition, we will find the upper and lower quartiles (Q3 and Q1, respectively), and the maximum and minimum values:

```{r summarize_rank}
fight_songs %>%
  summarise(min = min(rank), Q1 = quantile(rank, 0.25),
            median = median(rank), Q3 = quantile(rank,
                                                 0.75),
            max = max(rank), IQR = IQR(rank))
```

Based on the histogram, it is clear that the shape of the data is unimodal. The distribution is skewed to the right, with more colleges having higher ranked teams than lower ranked teams. The center (median) occurs at 34, and the spread (IQR) is 38, indicating that there is a moderate amount of variability in rankings. There is one outlier (a college football team ranked higher than 112) with a rank of 120. 

We hypothesize that a statistically significant relationship exists between `victory_win_won` and `rank` because it is reasonable to asssume historically successful college football teams would incorporate symbolic elements of their dominance into their iconic fight songs. In this case, we believe the words "victory", "win", and "won" are symbolic elements of dominance, giving us reason to believe higher-ranked teams are more likely to have their fights songs include these words. 

First, I will find the median rankings based on `victory_win_won` (yes or no):

```{r med_rank_victory_win_won}
fight_songs %>%
  group_by(victory_win_won) %>%
  summarise(med_rank = median(rank))
```

I observe a difference of 5.5 (37.5 - 32.0) in rank between colleges with and without "victory", "win", or "won" in their fight songs.

The null hypothesis is that there is no difference in the median rankings of college football teams between those with and without "victory", "win", or "won" in their fight songs; H0: mu(victory_win_wonNo) - mu(victory_win_wonYes) = 0.

The alternative hypothesis is that there is a difference in the median rankings of college football teams between those with and without "victory", "win", or "won" in their fight songs; H0: mu(victory_win_wonNo) - mu(victory_win_wonYes) ≠ 0.

Now, I will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the median rankings of college football teams who include "victory", "win", or "won" in their fight songs and those who do not:

```{r rank_victory_win_won_hyp_test}
obs_diff_victory_win_won <- 5.5 # From above code chunk

set.seed(11101962)
null_dist_victory_win_won <- fight_songs %>%
  specify(response = rank, explanatory = victory_win_won) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", 
            order = c("No", "Yes"))

get_p_value(null_dist_victory_win_won, obs_stat = obs_diff_victory_win_won, direction = "two_sided")

visualise(null_dist_victory_win_won) + 
  labs(title = "Null Distribution for Median Rankings of College Football Teams",
       subtitle = "For fight songs which include 'victory', 'win', or 'won'",
       x = "Sample Median Ranking",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_victory_win_won, direction = "two_sided")
```

Since the p-value, 0.634, is greater than our significance level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis. In other words, the data do not provide convincing evidence of a difference in the median rankings of college football teams based on whether or not their fight songs include the words "victory", "win", or "won". Thus, our original hypothesis was incorrect.

We also hypothesize that a statistically significant relationship exists between `opponents` and `rank` since higher-ranked college football teams are likely to have developed more emotionally-charged rivalries with their highly successful peers. With such long-standing, emotional rivalries, it is reasonable to believe fight songs associated with these highly-ranked college football programs allude to their rivals by name. 

First, I will find the median rankings based on `opponents` (yes or no):

```{r med_rank_opponents}
fight_songs %>%
  group_by(opponents) %>%
  summarise(med_rank = median(rank))
```

I observe a difference of 0.5 (34.5 - 34.0) in rank between colleges that do and do not mention opponents in their fight songs.

The null hypothesis is that there is no difference in the median rankings of college football teams between those who do and do not mention their opponents in their fight songs; H0: mu(opponentsNo) - mu(opponentsYes) = 0.

The alternative hypothesis is that there is a difference in the median rankings of college football teams between those who do and do not mention their opponents in their fight songs; H0: mu(opponentsNo) - mu(opponentsYes) ≠ 0.

Now, I will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the median rankings of college football teams who mention their opponents in their respective fight songs and those who do not:

```{r rank_opponents_hyp_test}
obs_diff_opponents <- 0.5 # From above code chunk

set.seed(11101962)
null_dist_opponents <- fight_songs %>%
  specify(response = rank, explanatory = opponents) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", 
            order = c("Yes", "No"))

get_p_value(null_dist_opponents, obs_stat = obs_diff_opponents, direction = "two_sided")

visualise(null_dist_opponents) + 
  labs(title = "Null Distribution for Median Rankings of College Football Teams",
       subtitle = "For fight songs which mention opponents",
       x = "Sample Median Ranking",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_opponents, direction = "two_sided")
```

Since the p-value, 1, is greater than our alpha level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis. In other words, the data do not provide convincing evidence of a difference in the median rankings of college football teams based on whether or not their fight songs mention opponents. Thus, our original hypothesis was incorrect.

Moreover, we hypothesize that a statistically significant relationship exists between `nonsense` and `rank` because there have been a plethora of articles written about how, in the past, highly successful teams included nonsensical phrases in their fight songs to distract the players on opposing college football teams. Since the fight songs included in our dataset were written decades ago (as evidenced by the `year` variable), it is reasonable to assume the songs associated with the historically-best college teams will have a higher likelihood of including nonsense (e.g "Hooperay"). 

First, I will find the median rankings based on `nonsense` (yes or no):

```{r med_rank_nonsense}
fight_songs %>%
  group_by(nonsense) %>%
  summarise(med_rank = median(rank))
```

I observe a difference of 11.5 (42.5 - 31) in rank between colleges with and without nonsense words in their fight songs.

The null hypothesis is that there is no difference in the median rankings of college football teams between those with and without nonsense words in their fight songs: H0 = mu(nonsenseNo) - mu(nonsenseYes) = 0.

The alternative hypothesis is that there is a difference in the median rankings of college football teams between those with and without nonsense words in their fight songs: H0 = mu(nonsenseNo) - mu(nonsenseYes) ≠ 0.

Now, I will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in median rank between colleges with/without nonsense words in their fight songs:

```{r rank_nonsense_hyp_test}
obs_diff_nonsense <- 11.5 # From above code chunk

set.seed(11101962)
null_dist_nonsense <- fight_songs %>%
  specify(response = rank, explanatory = nonsense) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", 
            order = c("Yes", "No"))

get_p_value(null_dist_nonsense, obs_stat = obs_diff_nonsense, direction = "two_sided")

visualise(null_dist_nonsense) + 
  labs(title = "Null Distribution for Median Rankings of College Football Teams",
       subtitle = "For fight songs which include nonsensical phrases",
       x = "Sample Median Ranking",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_nonsense, direction = "two_sided")
```

Since the p-value, 0.344, is greater than our alpha level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis. In other words, the data do not provide convincing evidence of a difference in the median rankings of college football teams based on whether or not their fight songs include nonsense words. Thus, our original hypothesis was incorrect.

Finally, we hypothesize that there is no statistically significant relationship between `rah` and `rank` since "rah" seems like it would be a common word in a fight song, irrespective of the quality (how successful) of a college football team.

First, I will find the median rankings based on `rah` (yes or no):

```{r med_rank_rah}
fight_songs %>%
  group_by(rah) %>%
  summarise(med_rank = median(rank))
```

I observe a difference of 5.5 (37.5 - 32.0) in rank between colleges with and without "rah" in their fight songs.

The null hypothesis is that there is no difference in the median rankings of college football teams between those with and without "rah" in their fight songs; H0: mu(rahNo) - mu(rahYes) = 0.

The alternative hypothesis is that there is a difference in the median rankings of college football teams between those with and without "rah" in their fight songs: Ha = mu(rahNo) - mu(rahYes) ≠ 0.

Now, I will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in median rankings between colleges with/without "rah" in their fight songs:

```{r rank_rah_hyp_test}
obs_diff_rah <- 5.5 # From above code chunk

set.seed(11101962)
null_dist_rah <- fight_songs %>%
  specify(response = rank, explanatory = rah) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", 
            order = c("Yes", "No"))

get_p_value(null_dist_rah, obs_stat = obs_diff_rah, direction = "two_sided")

visualise(null_dist_rah) + 
  labs(title = "Null Distribution for Median Rankings of College Football Teams",
       subtitle = "For fight songs which include 'rah'",
       x = "Sample Median Ranking",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_rah, direction = "two_sided")
```

Since the p-value, 0.678, is greater than our significance level of 0.05, we fail to reject the null hypothesis. In other words, the data do not provide convincing evidence of a difference in the median rankings of college football teams based on whether or not their fight songs include "rah". Therefore, our original hypothesis was correct.

Now, let’s find the full linear model that predicts the rank of a college football team (`rank`) based on various characteristics of the college's fight song: `victory_win_won`, `opponents`, `nonsense`, and `rah` and calculate the R-squared value for this model:

```{r rank_full_model}
(m_rank_full <- lm(rank ~ victory_win_won + opponents + nonsense + rah, data = fight_songs)) %>%
  tidy() %>%
  select(term, estimate)

glance(m_rank_full)$AIC
glance(m_rank_full)$r.squared
```

Based on the output, the full linear model is `rank-hat` = 39.0 - 6.25 * `victory_win_wonYes` - 5.56 * `opponentsYes` + 10.6 * `nonsenseYes`+ 6.80 * `rahYes`. The R-squared value is `r glance(m_rank_full)$r.squared`, which means that approximately `r 100*glance(m_rank_full)$r.squared`% of the variability in rank can be accounted for by the model. Given this R-squared value, the model is very weak since, in general, the closer the R-squared value is to 1 (100% of the variability in rankings can be explained by the model), the more accurate and useful the final model is. As the model only accounts for a small percent of the variability in rank, it is not a great predictor of a college football team's ranking.

The intercept tells us that for a college with "No" responses for `victory_win_won`, `opponents`, `nonsense`, and `rah`, the expected ranking of the school's football team is 39.0. The slope coefficient associated with `victory_win_wonYes` tells us that, if a fight song includes the words "victory", "win", or "won", the ranking of the football team is expected, on average, to decrease by 6.25, holding all else constant. The slope coefficient associated with `opponentsYes` tells us that, if a fight song mentions the college's opponent, the ranking of the football team is expected, on average, to decrease by 5.56, holding all else constant. The slope coefficient associated with `nonsenseYes` tells us that, if a fight song includes any nonsense words, the ranking of the football team is expected, on average, to increase by 10.6, holding all else constant. The slope coefficient associated with `rahYes` tells us that, if a fight song includes the word "rah", the ranking of the football team is expected, on average, to increase by 6.80, holding all else constant. 

To confirm that there is no better model, we will use the `step()` function and backwards selection with AIC as the selection criterion:

```{r rank_best_model, results = "hide"}
best_rank_model <- step(m_rank_full, direction = "backward")
```

```{r display_best_rank_model}
best_rank_model %>%
  tidy() %>%
  select(term, estimate)
glance(best_rank_model)$AIC
```

Since backwards selection removed `victory_win_won`, `opponents`, `nonsense`, and `rah` from our model, we should conclude that these four variables are poor predictors for the ranking of a college football team.

However, we must consider one last element before concluding that `victory_win_won`, `opponents`, `nonsense`, and `rah` are poor predictors of `rank`: whether the requirements for linear regression are satisfied. Amongst other things, a linear model mandates a continuous numerical response variable! But, it is clear that `rank` does not fulfill this criterion since it is a counting (discrete) numerical response variable. Thus, our final conclusions are as follows: this method of analysis involving linear regression is invalid and there is no guarantee that the explanatory variables are poor predictors of the response variable.

## Additional Analysis

Next, we will add a new variable to the `fight_songs` dataset called `region`, which will represent the region of the United States that a given college is located based on its conference -- north, west, south, or east. Since Notre Dame is the only college we will consider in the analysis that is independent (not in a conference), we will encode it to a region on its own:

```{r create-region-variable}
fight_songs <- fight_songs %>%
  mutate(region = case_when(
    conference == "SEC" ~ "south",
    conference == "Pac-12" ~ "west",
    conference == "Big 12" ~ "south",
    conference == "ACC" ~ "east",
    conference == "Big Ten" ~ "north",
    school == "Notre Dame" ~ "north"
  ))
```

Now, we will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the median number of times fights are mentioned between colleges located in the south versus those located in the north. The observed difference in medians is as follows:

```{r north_south_fights_diff_in_medians}
fight_songs %>%
  filter(region %in% c("north", "south")) %>%
  group_by(region) %>%
  summarise(med_fights = median(number_fights))
```

Based on the output above, we can see that the observed difference in the median number of times fights are mentioned between colleges in the south versus those located in the north is `r 3-1`. Now, we can conduct the hypothesis test.

The null hypothesis is that there is no difference in the median number of times fights are mentioned between colleges in the south versus those located in the north; H0: median(south) - median(north) = 0.

The alternative hypothesis is that there is a difference in the median number of times fights are mentioned between colleges in the south versus those located in the north; Ha: median(south) - median(north) ≠ 0.

We hypothesize that a statistically significant relationship exists between `region` and `number_fights` because there is a difference in the proportion of colleges in the north that mention fights (in their fight songs) versus those that mention fights in the south (0.66 versus 0.79, respectively). Therefore, we believe that, since a higher proportion of southern colleges mention fights in their songs than northern colleges, southern colleges will mention fights more times in their songs than northern colleges (we will reject the null hypothesis). For this reason, we will set the direction operator in the `get_p_value()` function to "left," because we predict that the median number of fights for southern colleges will be greater than that of the north (north - south should be negative, hence left).

```{r north_south_fights_hyp_test}
obs_diff_north_south <- 2 # From above code chunk

set.seed(11101962)
null_dist_north_south <- fight_songs %>%
  filter(region %in% c("north", "south")) %>%
  specify(response = number_fights, explanatory = region) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("south", "north"))

get_p_value(null_dist_north_south, obs_stat = obs_diff_north_south, direction = "left")

visualise(null_dist_north_south) + 
  labs(title = "Null Distribution for Median Number of Times Fights Are Mentioned",
       subtitle = "For colleges located in the north and south",
       x = "Sample Median Ranking",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_north_south, direction = "left")
```

Since the p-value, 0.835, is greater than our significance level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis. In other words, the data do not provide convincing evidence of a difference in the median number of times fights are mentioned in the fight songs of northern versus southern colleges. Thus, our original hypothesis was incorrect.

Next, we will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the mean duration of fight songs between colleges in the east versus those located in the west. The observed difference in means is as follows:

```{r east_west_duration_diff_in_means}
fight_songs %>%
  filter(region %in% c("east", "west")) %>%
  group_by(region) %>%
  summarise(mean = round(mean(sec_duration), 2))
```

Based on the output above, we can see that the difference in the mean duration of fight songs between colleges in the east versus those located in the west is `r 73.6 - 71.5`. Now, we can conduct the hypothesis test.

The null hypothesis is that there is no difference in the mean duration of fight songs between colleges in the east versus those located in the west; H0: mean(east) - mean(west) = 0.

The alternative hypothesis is that there is a difference in the mean duration of fight songs between colleges in the east versus the west; Ha: mean(east) - mean(west) ≠ 0.

We hypothesize that there is no statistically significant relationship between `sec_duration` and `region` because nearly all of the fight songs were created very long ago (as evidenced by the `year` variable), and there is no reason why fight songs associated with teams in one region would consistently be longer or shorter than those associated with college football teams of another region. Moreover, some colleges have relocated over time and their fight songs (which were created very long ago) have remained the same throughout.

```{r east_west_fights_hyp_test}
obs_diff_east_west <- 2.1 # From code chunk above

set.seed(11101962)
null_dist_east_west <- fight_songs %>%
  filter(region %in% c("east", "west")) %>%
  specify(response = sec_duration, explanatory = region) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("east", "west"))

get_p_value(null_dist_east_west, obs_stat = obs_diff_east_west, direction = "two_sided")

visualise(null_dist_east_west) + 
  labs(title = "Null Distribution for Average Duration of Fight Songs",
       subtitle = "For colleges located in the east and west",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_east_west, direction = "two_sided")
```

Since the p-value, 0.788, is greater than our significance level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis. In other words, the data do not provide convincing evidence of a difference in the mean duration of fight songs between colleges located in the east versus those located in the west. Therefore, our original hypothesis was correct.