---
title: "Analyzing College Fight Songs"
author: "Power Ninja Data Turtles"
date: "10/25/19"
output: github_document
---

```{r load-tidyverse-and-data, include=FALSE}
library(tidyverse)

fight_songs <- read_csv("/cloud/project/data/fight-songs.csv")
fight_songs <- fight_songs %>%
  select(-X21)
```

### Section 1: Introduction

In our research project, we will be analyzing the fight songs of various college football teams to discover the patterns (similarities/differences) between them. More specifically, we will be examining the fight songs of all 65 teams located across the Power 5 sports conferences (Big 10, Big 12, ACC, Pac-12 and SEC). Our dataset, which is fittingly titled `fight-songs`, is a part of the fivethirtyeight package in R. Each observation in the set represents a distinct Power 5 college football team. For each team (observation), the dataset features 23 variables (of which we are using 19, plus one of our own, for a total of 20), which contain a wide range of information, primarily concerning the school’s fight song. 
  
The variables are as follows: `school`, `conference`, `song_name`, `writers`, `year`, `student_writer`, `official_song`, `bpm`, `sec_duration`, `fight`, `number_fights`, `victory_win_won`, `rah`, `nonsense`, `colors`, `men`, `opponents`, `spelling`, `trope_count`, and finally, `rank`. Detailed explanations of each variable are located in the codebook.
  
The data was collected by looking at the lyrics of each song (as published by the school), metadata about each fight song on Spotify, history about each song (as stated by the school), and information about each school’s conference, which is easily accessible on the Internet. We added the `rank` variable to the dataset using Microsoft Excel, and we found this information from the Associated Press’s historic rankings of every college football team in the country, which was released last year.
  
### Section 2: Exploratory Data Analysis

We are interested in determining whether the number of times a fight song contains the word "fight" varies based on conference. Depending on the number of times this word appears, we can predict whether a particular conference is more or less aggressive than another conference. First, let's analyze the variable `number_fights`, which counts the number of times "fight" appears in the fight song for each team. A histogram displaying the number of occurrences of this word is shown below:

```{r histogram_number_fights}
ggplot(data = fight_songs, mapping = aes(x = number_fights)) + 
  geom_histogram(binwidth = 1) + 
  labs(x = "Occurrences of 'fight' in Fight Songs", y = "Number of Songs", title = "Number of Occurrences of 'fight'")
```

Let's also calculate the summary statistics for this distribution. Specifically, we will use the median as a measure of center and the interquartile range as a measure of spread (due to the skewness of the distribution). In addition, we will find the upper and lower quartiles (Q3 and Q1 respectively), and the maximum and minimum values:

```{r number_fights_summary_stats}
fight_songs %>%
  summarise(median = median(number_fights), 
            IQR = IQR(number_fights), 
            Q1 = quantile(number_fights, 0.25), 
            Q3 = quantile(number_fights, 0.75), 
            min = min(number_fights), 
            max = max(number_fights))
```

Based on the histogram, the shape of the distribution is clearly skewed to the right, implying that there are more songs that say "fight" only a few times compared to those that say "fight" multiple times. The distribution is clearly unimodal with one distinct peak located near x = 0 (zero occurrences of 'fight'). The center (median) of the distribution occurs x = 2 ('fight' appears twice), indicating that at least 50% of the songs contain 2 or less occurrences of this word. The data is fairly spread out, as indicated by an IQR of 5 and a range (maximum value minus minimum value) of 17. There are 2 outliers, which are the songs in which 'fight' appears at least 12.5 times (obviously, a word cannot occur at half-integer frequencies, so the songs must contain this word at least 13 times to move beyond Q3 + 1.5 * IQR).

Now, let's analyze the distribution of the number of times a song includes "fight," amongst the Power Five college football conferences (ACC, Big Ten, Pac-12, SEC, and Big 12) and Independent teams. The box plot of `number_fights` by `conference` is below:

```{r box_plot_fights_by_conference}
  ggplot(data = fight_songs, mapping = aes(y = number_fights, x = fct_reorder(factor(conference), number_fights))) +
  geom_boxplot() +
  labs(x = "College Football Conference", y = "Occurrences of 'fight' in Fight Songs", title = "Distribution of Occurrences of 'fight' in Fight Songs by College Conferences")
```

Let's also calculate the summary statistics for each boxplot. Specifically, we will use the median as a measure of center and IQR as a measure of spread. In addition, we will find the maximum and minimum values:

```{r fights_by_conference_summary_stats}
fight_songs %>%
  group_by(factor(conference)) %>%
  summarise(median = median(number_fights), 
            iqr = IQR(number_fights), 
            min = min(number_fights), 
            max = max(number_fights)) %>%
  arrange(median)
```

Based on the boxplots, we can see that the number of times that a fight song contains the word "fight" varies based on conference. The conferences with the highest median occurrences of "fight" are Big 12 and then SEC, while the conferences with the lowest median occurrences of "fight" are the ACC and then Big Ten.

### Section 3: Research Questions

From the univariate summary statistics and visualization (histogram) in Section 2, we learned, in the majority of college fight songs, the word "fight" appears only a few times. Moreover, the bivariate summary statistics and visualization (boxplots) revealed that the frequency of "fight" in fight songs is dependent on the particular conference a college belongs to. For instance, Louisiana State University, or LSU as it appears in the `fight_songs` dataset, is a member of the SEC conference. Thus, LSU's fight song is predicted to have a relatively large number of occurrences of "fight", since SEC has the second highest median occurrences of this word amongst the conferences considered.

We would like to investigate the research question: which characteristics, if any, of fight songs are exclusive to particular college football conferences, and which characteristics, if any, correlate to universal attributes of fights songs across the entire set of observations (all 65 colleges considered)? As explained previously, we have shown the number of occurrences of the word "fight" in fight songs is indeed associated with specific conferences. The predictor variables we anticipate using are: `nonsense`, `victory_win_won`, `colors`, and `opponents`. We will describe the relationship, if any exists, between these four predictor (X) variables and the response (Y) variable, `conference`. We hypothesize that a statistically significant relationship exists between `opponents` and `conference` since college football teams within the same conference often compete against one another, naturally leading to intense rivalries. Since conferences and iconic fight songs have both existed for decades, as evidenced by the `year` variable, it is reasonable to assume fight songs might reference rival teams. We hypothesize that there is no statistically significant relationship between `victory_win_won` and `conference` since different conferences have dominated college football over the years. If we make the assumption that many different teams within these conferences have been successful, then it is reasonable to believe the most fight songs will include at least one of the following words: "victory", "win", or "won". We hypothesize that a statistically significant relationship does not exist between `colors` and `conference` since mentioning a school's colors in a college football fight song seems like a common occurrence, regardless of which conference the teams belong to. We hypothesize that a statistically significant relationship exists between `nonsense` and `conference` because, since each conference corresponds to a different geographic region within the United States, teams from different conferences may have different cultural norms (and regional slang). Consequently, certain conferences may include teams with fight songs incorporating nonsense words while others do not at the same frequency. 

Our second research question is: how do characteristics of fight songs of higher-ranked (more successful) college football teams compare to those of their less successful counterparts? We will utilize the `rank` variable to form connections between the performances of certain college football teams and their respective fight songs. As a result, we will be better equipped to formulate conclusions about the similarities in the fight songs of higher-ranked (more successful) teams. The predictor variables we are interested in are: `victory_win_won` and `opponents`. We aim to describe the relationship, if any exists, between these two predictor (X) variables and the response (Y) variable, `rank`. We hypothesize that a statistically significant relationship exists between `victory_win_won` and `rank` because it is reasonable to asssume historically successful college football teams would incorporate symbolic elements of their dominance into their iconic fight songs. In this case, we believe the words "victory", "win", and "won" are symbolic elements of dominance, giving us reason to believe higher-ranked teams are more likely to have their fights songs include these words. We hypothesize that a statistically significant relationship exists between `opponents` and `rank` since higher-ranked college football teams are likely to have developed more emotionally-charged rivalries with their highly successful peers. With such long-standing, emotional rivalries, it is reasonable to believe fight songs associated with these highly-ranked college football programs allude to these rivals by name.

### Section 4: Data

Below, we use the glimpse() function to display a preview of the dataset `fight_songs`:

```{r glimpse_fight_songs}
glimpse(fight_songs)
```
