---
title: "Analyzing College Fight Songs"
author: "Power Ninja Data Turtles"
date: "10/25/19"
output: github_document
---

```{r load-tidyverse-and-data, include=FALSE}
library(tidyverse)
library(broom)

fight_songs <- read_csv("/cloud/project/data/fight-songs.csv")
fight_songs <- fight_songs %>%
  select(-X21)
```

### Section 1: Introduction

In our research project, we will be analyzing the fight songs of various college football teams to discover whether a song's tempo or duration can tell us anything about the content of the song and whether a team's fight song is indicative of their college football program's success. More specifically, we will be examining the fight songs of all 65 teams located across the Power 5 sports conferences (Big 10, Big 12, ACC, Pac-12 and SEC) plus Notre Dame (Independent conference). Hence, our dataset, which is fittingly titled `fight-songs`, includes 65 observations. Each observation in the set represents a distinct Power 5 college football team (or Notre Dame). For each team (observation), the original dataset featured 23 variables. However, we plan to use 19 of these variables, plus one of our own, for a total of 20. The variables primarily contain information regarding the school’s fight song, as well as a couple of characteristics of the college football teams themselves (i.e. which conference they belong to).
  
The variables are as follows: `school`, `conference`, `song_name`, `writers`, `year`, `student_writer`, `official_song`, `bpm`, `sec_duration`, `fight`, `number_fights`, `victory_win_won`, `rah`, `nonsense`, `colors`, `men`, `opponents`, `spelling`, `trope_count`, and finally, `rank`. Detailed explanations of each variable are located in the codebook.
  
The data was collected by looking at the lyrics of each song (as published by each individual college), metadata about each fight song on Spotify, history about each song (as stated by the college), and information about each school’s conference, which is easily accessible on the Internet. We added the `rank` variable to the dataset using Microsoft Excel, and we found this information from the Associated Press’s historic rankings of every college football team in the country, which was released last year.

As as note, some schools may have more than one fight song, and some of the songs sanctioned as "official" by their schools are not the ones that fans most commonly chant. The songs that seemed best-known and best-loved were chosen as the "official" fight song. Additionally, fivethirtyeight has tailored the lyrics of certain fight songs to those sung most regularly and published by the school. Thus, some verses will not appear (and hence will not be considered in our analysis).
  
### Section 2: Exploratory Data Analysis

We are interested in figuring out whether a team's tempo (measured in bpm, or beats per minute) has anything to do with the number of clichés that a song has. First, we will create a histogram and calculate the summary statistics to visualize the distribution of tempos across fight songs for all teams in our dataset:

```{r histogram-bpm}
ggplot(data = fight_songs, mapping = aes(x = bpm)) + 
  geom_histogram(binwidth = 10) + 
  labs(x = "Tempo (bpm)", y = "Number of Songs", title = "Tempos of Fight Songs of College Football Teams")
```

Let's also calculate the summary statistics for this distribution. Specifically, we will use the median as a measure of center and the interquartile range as a measure of spread (due to the bimodal nature of the distribution). In addition, we will find the upper and lower quartiles (Q3 and Q1, respectively), and the maximum and minimum values:

```{r number_fights_summary_stats}
fight_songs %>%
  summarise(median = median(bpm), 
            IQR = IQR(bpm), 
            Q1 = quantile(bpm, 0.25), 
            Q3 = quantile(bpm, 0.75), 
            min = min(bpm), 
            max = max(bpm))
```

Based on the histogram, it is clear that the shape of the data is clearly bimodal, with two distinct peaks occurring around 40 bpm and around 150 bpm. There are more songs that are clustered around the higher bpm mode. The center (median) occurs at 140 bpm, and the spread (IQR) is 61 bpm, indicating that there is a moderate amount of variability in tempos. There are no outliers in this distribution. Due to the bimodal result, it seems like there is a natural grouping between "slow" songs and "fast" songs, which we will exploit in future analyses.

Now, let's see whether there appears to be a relationship between a fight song's tempo (bpm) and the number of clichés (tropes) that a song has. We will do this by creating a scatterplot and fitting a linear model:

```{r scatterplot-bpm-tropes}
ggplot(data = fight_songs, mapping = aes(x = bpm, y = trope_count)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Tempo (bpm)", y = "Number of Clichés", title = "Number of Clichés vs. Tempo")
```

There seems to be a weak, negative linear relationship between tempo and number of clichés. Let's find the linear model associated with this scatterplot:

```{r m_bpm}
(m_bpm <- lm(data = fight_songs, trope_count ~ bpm)) %>%
  tidy() %>%
  select(term, estimate)
```

Based on the output, the linear model that predicts number of tropes based on tempo is: trope_count-hat = 4.59 - 0.00759 * bpm. The intercept tells us that if a song has 0 bpm (nonsensical), it is expected to have 4.59 clichés (tropes), on average. The slope tells us that for an increase in 1 bpm, the expected number of clichés is predicted, on average, to decrease by 0.00759. The R-squared value of this model is `r glance(m_bpm)$r.squared`, meaning that approximately `r glance(m_bpm)$r.squared*100` percent of the variability in clichés is accounted for by the linear model. This means that the linear model is relatively weak since, the closer the R squared value is to 1 (or 100% variability), the more accurate the model is.

Now, let's see whether `trope_count` is related as to the `rank` (success) of a team. We will do this by creating another scatterplot and fitting a model:

```{r scatterplot-tropes-rank}
ggplot(data = fight_songs, mapping = aes(x = trope_count, y = rank)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Number of Clichés in Fight Song", y = "Historical College Football Team Ranking", title = "Historical College Football Team Ranking vs. Number of Clichés")
```

There seems to be a weak positive linear relationship between number of clichés in a fight song and the historical ranking of a college football team. Let's find the linear model associated with this scatterplot:

```{r m_tropes-rank}
(m_tropes_rank <- lm(data = fight_songs, rank ~ trope_count)) %>%
  tidy() %>%
  select(term, estimate)
```

Based on the output, the linear model that predicts rank based on number of clichés is: rank-hat = 35.6 + 0.545 * trope_count. The intercept tells us that if a song has 0 clichés, it is expected to have a ranking of 35.6, on average. The slope tells us that for an increase in 1 cliché, the historical college football team ranking is predicted, on average, to increase by 0.545 points. The R-squared value of this model is `r glance(m_tropes_rank)$r.squared`, meaning that approximately `r glance(m_tropes_rank)$r.squared*100` percent of the variability in ranks is accounted for by the linear model. This means that the linear model is extremely weak since, the closer the R squared value is to 1 (or 100% variability), the more accurate the model is.

### Section 3: Research Questions

Our first research question is: how does the tempo and duration of a college football team's fight song predict the content of the song (i.e. the number of clichés/tropes)? We will utilize the `trope_count` variable, which counts the number of clichés in a fight song (since we define a cliché as whether a song contains the word "fight", the word "victory", the word "won", the word "win", the word "rah", nonsense syllables, school colors, a reference to "men"/"boys"/"sons", an opponent name, or spells something out), to form connections between a song's duration and tempo and its content. The predictor variables we are interested in are: `bpm`, which we started to explore in Section 2, and `sec_duration`. We aim to describe the relationship, if any exists, between the two numerical predictor (X) variables and the numerical response (Y) variable, `trope_count`. Based on the exploratory data analysis from Section 2, we hypothesize that the number of clichés will be less for songs with slower tempos (smaller `bpm`) and probably shorter durations (smaller `sec_duration`). We think that longer songs will contain more clichés because there is more time to fill the lyrics with clichés. Without completing the data analysis in Section 2, we would have thought that faster tempos would lead to more clichés, like "fight" or "rah," because faster tempos are generally related to higher energies.  We think that there may be confounding variables, so we want to look at tempo and duration together. Combining tempo and duration, we hope to separate songs into 4 categories, "short and fast," "short and slow", "long and fast," and "long and slow", and thus compare the number of tropes across these four categories.

Our second research question is: how do characteristics of fight songs of college football teams correspond to their respective historical levels of success? We will utilize the `rank` variable to form connections between the performances of college football teams and their respective fight songs. The predictor variables we are interested in are: `victory_win_won`, `opponents`, `nonsense`, and `rah`. We aim to describe the relationship, if any exists, between these four categorical predictor (X) variables and the numerical response (Y) variable, `rank`. We hypothesize that a statistically significant relationship exists between `victory_win_won` and `rank` because it is reasonable to asssume historically successful college football teams would incorporate symbolic elements of their dominance into their iconic fight songs. In this case, we believe the words "victory", "win", and "won" are symbolic elements of dominance, giving us reason to believe higher-ranked teams are more likely to have their fights songs include these words. We also hypothesize that a statistically significant relationship exists between `opponents` and `rank` since higher-ranked college football teams are likely to have developed more emotionally-charged rivalries with their highly successful peers. With such long-standing, emotional rivalries, it is reasonable to believe fight songs associated with these highly-ranked college football programs allude to these rivals by name. Moreover, we hypothesize that a statistically significant relationship exists between `nonsense` and `rank` because there have been a plethora of articles written about how, in the past, highly successful teams included nonsensical phrases in their fight songs to distract the players on the opposing college football teams. Since the fight songs included in our dataset were written decades ago (as evidenced by the `year` variable), it is reasonable to assume the songs associated with the historically-best college teams will have a higher likelihood of including nonsense (e.g "Hooperay"). Finally, we hypothesize there is no statistically significant relationship between `rah` and `rank` since "rah" seems like it would be a common word in a fight song, irrespective of the quality (how successful) of a college football team.

### Section 4: Data

Below, we use the glimpse() function to display a preview of the dataset `fight_songs`:

```{r glimpse_fight_songs}
glimpse(fight_songs)
```
