---
title: "Analyzing College Fight Songs"
author: "Power Ninja Data Turtles"
date: "10/25/19"
output: github_document
---

```{r load-tidyverse-and-data, include=FALSE}
library(tidyverse)

fight_songs <- read_csv("/cloud/project/data/fight-songs.csv")
fight_songs <- fight_songs %>%
  select(-X21)
```

### Section 1. Introduction

### Section 2. Exploratory data analysis

We are interested in learning whether the number of times that a fight song contains the word "fight" varies based on conference, as the more times "fight" is said might predict whether a conference as a whole is more or less aggressive than another conference. First, let's analyze the variable number_fights, which counts the number of times a song says "fight," for all the teams. The histogram of number_fights is below:

```{r histogram-number_fights}
ggplot(data = fight_songs, mapping = aes(x = number_fights)) + 
  geom_histogram(binwidth = 1) + 
  labs(x = "Occurrences of 'Fight'", y = "Number of Fight Songs")
```

### Section 3. Research questions

### Section 4. Data

Below is a glimpse of the data set fight_songs:

```{r glimpse-fight_songs}
glimpse(fight_songs)
```
