---
title: "Rah! Fight! Win!: Analyzing the Nonsensical Nature of College Fight Songs"
author: "Power Ninja Data Turtles"
date: "12/13/19"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-data-and-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(infer)
library(broom)

fight_songs <- read_csv("/cloud/project/data/fight-songs.csv")
fight_songs <- fight_songs %>%
  select(-X21)
```

### Statistical Methods Used

For our data analysis, we used a combination of hypothesis tests and a variety of plots (from the `ggplot` package) in order to visualize and interpret each question. 

We used hypothesis tests because finding the p-value for each instance allowed us to conclude whether or not the data provided convincing evidence of a trend, such as the relationship between the tempo and content of songs. Our hypothesis tests were conducted using simulation instead of the CLT. The CLT was not a valid option, as none of the subsets of the data set had at least 30 observations and the majority of our tests are for independence (difference between two groups).

Visualizing the relationships between the explanatory and response variables with plots made it easy for viewers to understand how the level or occurrence of certain variables changed based on differing factors between songs. We tried to use unique but clearly structured and labeled plot formats that would display information in a visually appealing way without confusing the viewer.

### Research Question 1: Predicting the Content of College Fight Songs Using Tempo and Duration

Our first research question is:

>"How does the tempo and duration of a college football team's fight song predict the content of the song, specifically the number of clichés/tropes?"

Before delving deeper into the analysis, we will first look at the distributions of the two explanatory variables, `bpm` and `sec_duration`.

Starting with `bpm`, which is a measure of a fight song's tempo, we will create a histogram of the distribution:

```{r histogram-bpm}
ggplot(fight_songs, mapping = aes(x = bpm)) +
  geom_histogram(binwidth = 10) +
  labs(title = "Tempo of College Fight Songs",
       x = "Beats per Minute (bpm)",
       y = "Number of Songs")
```

We will also calculate the summary statistics for this distribution. Specifically, we will use the median as a measure of center and the interquartile range as a measure of spread (due to the bimodal nature of the distribution). In addition, we will find the upper and lower quartiles (Q3 and Q1, respectively), and the maximum and minimum values:

```{r calc-summary-stats-bpm}
fight_songs %>%
  summarise(min = min(bpm),
            Q1 = quantile(bpm, 0.25),
            median = median(bpm),
            Q3 = quantile(bpm, 0.75),
            max = max(bpm),
            IQR = IQR(bpm))
```

Based on the histogram, it is clear that the shape of the data is clearly bimodal, with two distinct peaks occurring around 70 bpm and around 150 bpm, with a split in the data at around 100 bpm. There are more songs that are clustered around the higher bpm mode. The center (median) occurs at 140 bpm, and the spread (IQR) is 61 bpm, indicating that there is a moderate amount of variability in tempos. There are no outliers in this distribution. Due to the bimodal result, it seems like there is a natural grouping between “slow” songs and “fast” songs, so we will use the `mutate()` function to add a new variable, `tempo`, which is "slow" if a song's `bpm` is less than or equal to 100 bpm and "fast" if a song's tempo is greater than 100 bpm.

```{r mutate-tempo}
fight_songs <- fight_songs %>%
  mutate(tempo = case_when(
    bpm <= 100 ~ "slow",
    bpm > 100 ~ "fast"
  ))
```

Now, we will explore our second explanatory variable, `sec_duration`, which is the duration of a song in seconds. In order to do this, we will create a histogram of the distribution and find the relevant summary statistics (Q1, median, Q3, min, max, IQR):

```{r histogram-summary-stats-sec-duration}
ggplot(fight_songs, mapping = aes(x = sec_duration)) +
  geom_histogram(binwidth = 20) +
  labs(title = "Duration of College Fight Songs",
       x = "Duration (sec)",
       y = "Number of Songs")

fight_songs %>%
  summarise(min = min(sec_duration),
            Q1 = quantile(sec_duration, 0.25),
            median = median(sec_duration),
            Q3 = quantile(sec_duration, 0.75),
            max = max(sec_duration),
            IQR = IQR(sec_duration))
```

Based on the histogram, we can see that the distribution of fight song durations is roughly symmetric (slightly skewed to the right) and unimodal, with a peak at around 70. There are some outliers on the higher end of the spectrum (`sec_duration` > 125.5), indicating that these songs are significantly longer than the others. The center of the distribution occurs at around 67 seconds, and the IQR of the distribution is 27 seconds, which is relatively narrow, indicating that fight songs do not have dramatically different lengths. Like we did with `bpm`, let's add a new variable, `length`, which is "short" if a song is less than or equal to the median of 67 seconds and "long" if a song is greater than the median of 67 seconds.

```{r mutate-length}
fight_songs <- fight_songs %>%
  mutate(length = case_when(
    sec_duration <= 67 ~ "short",
    sec_duration > 67 ~ "long"
  ))
```

Now that we have a better understanding of our two explanatory variables, we want to add a new variable, `classify`, which combines `bpm` and `sec_duration` by labeling each song with one of four classifications: "slow and short", "slow and long", "fast and short", and "fast and long":

```{r mutate-classify}
fight_songs <- fight_songs %>%
  mutate(classify = case_when(
    tempo == "slow" & length == "short" ~ "slow and short",
    tempo == "slow" & length == "long" ~ "slow and long",
    tempo == "fast" & length == "short" ~ "fast and short",
    tempo == "fast" & length == "long" ~ "fast and long",
  ))

fight_songs %>%
  count(classify)
```

Based on the output displayed in the tibble above, 23 songs are categorized as "fast and long", 25 songs are categorized as "fast and short", 9 songs are categorized as "slow and long", and 8 songs are categorized as "slow and short".

Using these classifications, we will visualize the groups and fill in each observation with the number of tropes associated with that particular observation. We choose to use `geom_hline()` and `geom_vline()` to add horizontal and vertical reference lines to the jittered plot (`geom_jitter()` adds a small amount of random variation to the location of each point). We also choose to use `scale_color_gradientn()` to create a rainbow-colored gradient scale, which indicates the number of tropes for a given fight song.

```{r visualize-classify}
ggplot(fight_songs, mapping = aes(x = sec_duration, y = bpm)) +
  geom_jitter(aes(color = trope_count)) + 
  geom_hline(yintercept = 100, linetype = "dashed", color = "orange") +
  geom_vline(xintercept = 67, linetype = "dashed", color = "orange") +
  theme_minimal() +
  labs(title = "Classification of College Fight Songs", 
       subtitle = "By tempo and duration",
       x = "Duration (sec)",
       y = "Tempo (bpm)",
       color = "Number of Tropes") +
  scale_color_gradientn(colors = rainbow(5))
```

The upper left-hand region of the plot represents songs that are "fast and short" while the lower left-hand region represents songs that are "slow and short." The upper right-hand region of the plot represents songs that are "fast and long", and the lower right-hand region represents songs that are "slow and long".

Finally, we will explore our response variable, `trope_count`, which is a measure of the number of clichés/tropes in a given fight song. We will also use a histogram and summary statistics for this univariate analysis:

```{r histogram-summary-stats-trope-count}
ggplot(fight_songs, mapping = aes(x = trope_count)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Number of Clichés in College Fight Songs",
       x = "Number of Clichés",
       y = "Number of Songs")

fight_songs %>%
  summarise(min = min(trope_count),
            Q1 = quantile(trope_count, 0.25),
            median = median(trope_count),
            Q3 = quantile(trope_count, 0.75),
            max = max(trope_count),
            IQR = IQR(trope_count),
            sd = sd(trope_count))
```

Based on the histogram and summary statistics, we can see that the distribution for number of tropes is unimodal with a peak at around 4 and skewed slightly to the left. There is 1 outlier at the maximum value of our distribution (8 tropes). The center of the distribution, described by the median, is 4 tropes, and the IQR of 2 indicates that there is not a large amount of variability in the number of tropes for college fight songs.

Now, we will return to our research question by examining whether the amount of clichés varies based on a song's classification. First, we will create violin plots for the distribution of the number of tropes for each classification and add jitter. Using jittered points allows us to manage the effects of overplotting when working with smaller datasets. We were inspired to use this type of plot after conferencing with Dr. Eric Monson who delivered the "Tips for Effective Data Visualization" presentation earlier this semester.

```{r boxplots-summary-stats-number-tropes}
ggplot(fight_songs, mapping = aes(x = classify, y = trope_count)) +
  geom_violin(draw_quantiles = c(0.25, 0.50, 0.75)) +
  geom_jitter() +
  labs(title = "Number of Clichés",
       subtitle = "By Song Classification",
       x = "Song Classification",
       y = "Number of Clichés")

fight_songs %>%
  group_by(classify) %>%
  summarize(median = median(trope_count), IQR = IQR(trope_count), sd = sd(trope_count))
```

Not surprisingly, all of the distributions, except for "slow and long", are centered at 4 tropes, which is the median number of tropes for all songs in the dataset. However, there is one category, "slow and long," which has a median of 5. We would like to check whether this median is statistically significant or not. To do this, we will conduct a hypothesis test for the median number of tropes for songs that are considered "slow and long". Our null hypothesis is that the true median number of tropes for "slow and long" songs is 4, H0: median("slow and long") = 4. Our alternative hypothesis is that the true median number of tropes is different than 4, Ha: median("slow and long") ≠ 4. We will use a significance (alpha) level of 0.05. We will create and visualize the null distribution and calculate the associated p-value:

```{r hypothesis-test-slow-and-long}
obs_median <- 5 # From summary statistics in previous code chunk

slow_long <- fight_songs %>%
  filter(classify == "slow and long")

set.seed(11101962)
null_slow_long <- slow_long %>%
  specify(response = trope_count) %>%
  hypothesize(null = "point", med = 4) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median")

get_p_value(null_slow_long, obs_stat = obs_median, direction = "two_sided")

visualise(null_slow_long) + 
  labs(title = "Null Distribution for Median Number of Tropes",
       subtitle = "For Slow and Long Fight Songs",
       x = "Sample Median Number of Tropes",
       y = "Count") +
  shade_p_value(obs_stat = obs_median, direction = "two_sided")
```

Based on our p-value of 0.038, which is less than 0.05 (significance level), we reject the null hypothesis in favor of the alternative hypothesis; in other words, there is sufficient evidence that the true median number of tropes is different than 4. Thus, the data provide convincing evidence that the median number of tropes for songs that are slow and long is different than the population median of 4. However, our sample size is very small (9 observations), so we must be wary of our results and acknowledge the limitations of our conclusions.

We can also see from the visualization "Number of Clichés" that the spread for "slow and short" songs is much smaller compared to all other song classifications. We will test whether the standard deviation for "slow and short" songs is significantly different from the population standard deviation of 1.675. The null hypothesis is that the true standard deviation in the number of tropes for "slow and short" songs is 1.675, H0: sigma = 1.675. The alternative hypothesis is that the true standard deviation in the number of tropes for "slow and short" songs is less than 1.675, Ha: sigma < 1.675. We will use a significance level of 0.05.

```{r hypothesis-test-slow-and-short}
obs_sd <- 1.13 # From summary statistics in previous code chunk

slow_short <- fight_songs %>%
  filter(classify == "slow and short")

set.seed(11101962)
null_slow_short <- slow_short %>%
  specify(response = trope_count) %>%
  hypothesize(null = "point", sigma = 1.675) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "sd")

get_p_value(null_slow_short, obs_stat = obs_sd, direction = "left")

visualise(null_slow_short) + 
  labs(title = "Null Distribution for Standard Deviation of Tropes",
       subtitle = "For Slow and Short Fight Songs",
       x = "Sample Standard Deviation of Tropes",
       y = "Count") +
  shade_p_value(obs_sd, direction = "left")
```

Based on the p-value of 0.685, which is greater than our alpha level of 0.05, we fail to reject the null hypothesis in favor of the alternative hypothesis; in other words, the data do not provide convincing evidence that the true standard deviation for slow and short songs is less than the population standard deviation of 1.675.

Now, we will find the full linear model that predicts number of tropes (`trope_count`) from tempo (`bpm`) and duration (`sec_duration`):

```{r model-full-trope-count}
(m_full <- lm(trope_count ~ bpm + sec_duration, data = fight_songs)) %>%
  tidy() %>%
  select(term, estimate)
```

Based on the output, the full linear model is `trope_count-hat` = 4.58 - 0.00757 * `bpm` + 0.000208 * `sec_duration`. The R-squared value is `r glance(m_full)$r.squared`, which means that approximately `r glance(m_full)$r.squared *100`% of the variability in trope counts can be explained by the linear model that predicts trope count from a song's tempo and duration. Given this R-squared value, our model is very weak, since, in general, the closer the R-squared value is to 1 (100% of the variability in trope counts can be explained by the model), the more accurate and useful the final model is. As the model only accounts for a small percent of the variability in trope counts, it is not a great predictor of a fight song's trope count.

The intercept tells us that for a song with 0 bpm which lasts 0 seconds, the expected number of tropes is 4.58. But of course, this is nonsensical, since none of the fight songs we are considering in our analysis last 0 seconds (for that matter, no songs, by definition, last 0 seconds!). The slope coefficient associated with `bpm` tells us that for an increase in 1 bpm, the number of tropes is expected, on average, to decrease by 0.00757, holding all else constant. The slope coefficient associated with `sec_duration` tells us that for an increase in a song's duration by 1 second, the number of tropes is expected, on average, to increase by 0.000208, holding all else constant. 

Now, we will conduct a hypothesis test for the slopes to determine whether the slope coefficients for `bpm` and `sec_duration` are significantly different from 0. We will use a significance level of 0.05. Conducting a hypothesis test for the slopes will help us confirm or deny our research question on whether either tempo or duration are useful predictors of the content of a fight song, as determined by a song's number of tropes. 

Let our null hypotheses be that the slope coefficients associated with both variables are 0; H0: beta(`bpm`) = 0 and beta(`sec_duration`) = 0. Let our alternative hypotheses be that the slope coefficients associated with both variables are significantly different than 0, Ha: beta(`bpm`) ≠ 0 and beta(`sec_duration`) ≠ 0.

First, we will look at the slope of `bpm`, which we found to be 0.00757:

```{r hypothesis-test-bpm-slope}
obs_beta_bpm <- tidy(m_full) %>%
  select(estimate) %>% 
  slice(2) %>% 
  pull() 

set.seed(11101962)
null_dist_bpm_slope <- fight_songs %>%
  specify(response = trope_count, explanatory = bpm) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope")

get_p_value(null_dist_bpm_slope, obs_stat = obs_beta_bpm, direction = "two_sided")

visualise(null_dist_bpm_slope) + 
  labs(title = "Null Distribution for Tempo Slope Coefficient",
       subtitle = "In full linear model for trope count",
       x = "Sample bpm Slope Coefficients",
       y = "Count") +
  shade_p_value(obs_beta_bpm, direction = "two_sided")
```

Next, we will look at the slope of `tempo`, which we found to be 0.000208:

```{r hypothesis-test-sec-duration-slope}
obs_beta_sec_duration <- tidy(m_full) %>% 
  select(estimate) %>% 
  slice(3) %>%
  pull() 

set.seed(11101962)
null_dist_sec_duration_slope <- fight_songs %>%
  specify(response = trope_count, explanatory = sec_duration) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope")

get_p_value(null_dist_sec_duration_slope, obs_stat = obs_beta_sec_duration, direction = "two_sided")

visualise(null_dist_sec_duration_slope) + 
  labs(title = "Null Distribution for Song Duration Slope Coefficient",
       subtitle = "In full linear model for trope count",
       x = "Sample Song Duration Slope Coefficients",
       y = "Count") +
  shade_p_value(obs_beta_sec_duration, direction = "two_sided")
```

The p-values for the slope coefficients of `bpm` and `sec_duration` are 0.238 and 0.978, respectively. Since both p-values are greater than our alpha level of 0.05, we fail to reject the null hypotheses in favor of the alternative hypotheses. Hence, there appears to be insufficient evidence that the slope coefficients for `bpm` and `sec_duration` are different than 0. 

However, we must must verify that the four conditions for inference for regression are satisfied before finalizing any conclusions: (1) observations should be independent; (2) residuals should be randomly distributed around 0; (3) residuals should be nearly normally distributed, centered at 0; (4) residuals should have constant variance.

First, we can assume that the observations (fight songs) are independent because college fight songs are unique to every team and written by different authors.

Next, we will verify our assumption (confirm independence of observations) by plotting the residuals in the order of data collection:

```{r testing-condition-1}
m_full_aug <- augment(m_full)
ggplot(data = m_full_aug, aes(x = 1:nrow(m_full_aug), y = .resid)) +
  geom_point() +
  labs(title = "Residual Plot by Index",
       subtitle = "In the order of data collection",
       x = "Index",
       y = "Residual")
```

Next, let's examine the normality of residuals:

```{r testing-condition-3}
ggplot(data = m_full_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 1.25) +
  labs(title = "Normality of Residuals",
       x = "Residuals")
```

Finally, we will check the distribution of residuals around 0 and constant variance:

```{r testing-conditions-2-and-4}
ggplot(data = m_full_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, lty = 3, color = "blue") +
  labs(title = "Distribution of Residuals",
       x = "Predicted values, y-hat",
       y = "Residuals")
```

Clearly, condition 4 (constant variance) is violated. Therefore, inference for regression is invalid. This means our conclusion that there is insufficient evidence to suggest the slope coefficients for `bpm` and `sec_duration` are different than 0 is also not credible.

To confirm that there is no better linear model, we will use the `step()` function and backwards selection with AIC as the selection criterion:

```{r backwards-selection-trope-count, results = "hide"}
(m_trope_count <- step(m_full, direction = "backward")) 
```

```{r AIC-m-trope-count}
m_trope_count %>%
  tidy() %>%
  select(term, estimate)
```

Since backwards selection removed both `bpm` and `sec_duration` from our model, we should conclude that these two variables are not valid predictors for the number of tropes in a college fight song.

However, we must consider one last element before concluding that `bpm` and `sec_duration` are poor predictors of `trope_count`: whether the requirements for linear regression are satisfied. Amongst other things, a linear model mandates a continuous numerical response variable! But, it is clear that `trope_count` does not fulfill this criterion since it is a counting (discrete) numerical response variable. Thus, our final conclusions are as follows: this method of analysis involving linear regression is invalid and there is no guarantee that the explanatory variables are poor predictors of the response variable.

### Conclusion from Research Question 1

Circling back to our research question of whether a fight song's tempo and duration can help predict the content of a college fight song, as measured by the number of clichés, we hypothesized that the number of clichés would be less for songs with slower tempos (smalle `bpm`) and probably shorter durations (smaller `sec_duration`). We thought that longer songs would contain more clichés because there is more time to fill the lyrics with clichés. We thought that faster tempos, since they are generally related to higher energies, would have included more clichés.

From our exploratory data analysis, we noticed that there was a natural grouping in fight songs such that all fight songs could be classified as having a slow or fast tempo. With this information and with the results from exploring the duration variable, we decided to classify all fight songs into four categories: "short and fast," "short and slow," "long and fast," and "long and slow."

After creating a violin plot for each classification and its respective distribution of the number of tropes, we noticed two things. First, "slow and long" songs had a greater median number of tropes. Second, "slow and short" songs had a smaller variation in the number of tropes. From here, we decided to conduct a hypothesis test to confirm or deny whether what we observed in the violin plots was statistically significant. It turned out that "slow and long" songs in our data set did, in fact, have median number of tropes that was different than the the population median of 4 (p = 0.038). However, the small spread of the distribution of "slow and short" songs proved not to be different from the population standard deviation of 1.67 (p = 0.685).

Finally, we looked at the linear model between `bpm` and `sec_duration`, the explanatory variables, and `trope_count` to see whether `bpm` and `sec_duration` were, indeed, good predictors of the number of tropes in a college fight song. The original model had an R-squared value of 0.022608, which indicated that the model was very weak. After conducting hypothesis tests for the slope of `sec_duration` and `bpm`, we found that neither slope was significantly different than 0 (p = 0.238 and p = 0.978, respectively). However, after checking the conditions of inference for regression, we found that the residuals did not have constant variance; therefore, our inference for regression is invalid, and our conclusion that there is insufficient evidence to suggest the slope coefficients for `bpm` and `sec_duration` are different than 0 is not credible.

Finally, we used backwards selection using AIC as the criterion to see if there was a particularly better linear model. However, backwards selection removed both of our explanatory variables, `bpm` and `sec_duration`, which indicated to use that these two variables are not valid predictors for the number of tropes in a college fight song. Therefore, the answer to our research question is that neither tempo nor duration can predict the content of a college fight song. The only thing we can say is that "slow and long" fight songs have a different median number of tropes than other fight songs.

## Additional Analysis: Looking at Characteristics in Fight Songs in Northern and Southern Athletic Conferences

For the last part of our analysis, we are interested in examining whether certain characteristics of fight songs are regionally unique. In particular, we are interested in looking at the variables `victory_win_won`, whether a song includes the words "victory", "win", or "won, `men`, whether a song refers to male groups (fathers, sons, men, etc.), and `nonsense`, whether a song uses nonsense syllables, to see whether northern schools (conferences) are more or less likely to have fight songs with these characteristics.

First, we will add a new variable to the `fight_songs` dataset called `region`, which will represent the region of the United States that a given college is located based on its conference -- north or south. Since Notre Dame is the only college we will consider in the analysis that is independent (not in a conference), we will encode it to a region on its own (north).  It should also be noted that the PAC-12 and ACC conferences are considered western and eastern conferences, respectively, but for the purpose of our analysis, we will label them as northern and southern, respectively, because we are interested in the characteristics of fight songs for conferences in the north vs. south. Exactly half of the teams in the PAC-12 conference are, indeed, northern schools, while the majority of schools in the ACC conference are southern.

```{r create-region-variable}
fight_songs <- fight_songs %>%
  mutate(region = case_when(
    conference == "SEC" ~ "south",
    conference == "Pac-12" ~ "north",
    conference == "Big 12" ~ "south",
    conference == "ACC" ~ "south",
    conference == "Big Ten" ~ "north",
    school == "Notre Dame" ~ "north"
  ))

fight_songs %>%
  count(region)
```

There are 27 schools that we are considering to be in the northern region and 38 in the southern region.

We will look at our first variable, `victory_win_won` to see whether there exists a statistically significant relationship between the proportion of teams for which `victory_win_won` is "yes" for northern or southern conferences.  First, we will find what the two proportions are.

```{r calc-prop-yes-victory-win-won-n-s}
fight_songs %>%
  count(region, victory_win_won) %>%
  group_by(region) %>%
  mutate(prop_victory_win_won_yes = n/sum(n))
```

Based on the output, 70.4% of schools in northern conferences have the words "victory," "win," or "won" in their fight songs. On the other hand, only 57.9% of schools in southern conferences have the words "victory," "win," or "won" in their fight songs. We would like to see if this result is statistically significant and what the true difference in proportions is. We have to use simulation-based hypothesis testing because we are looking for the difference in proportions.

First, we will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the proportion of fight songs that say "victory," "win," or "won" for schools in northern vs. southern conferences. Our null hypothesis is that there is no difference in the proportion of schools that say "victory," "win," or "won" in their fight songs for southern and northern conferences, H0: p(southern) = p(northern). Our alternative hypothesis is that there is a difference in the proportion of schools that say "victory," "win," or "won" in their fight songs for southern and northern conferences, Ha: p(southern) ≠ p(northern). We will use a significance level of 0.05.

```{r hyp-test-victory-win-won}
obs_diff_props_n_s_victory <- 0.7037037	- 0.5789474 # From above code chunk

set.seed(11101962)
null_dist_north_south_victory <- fight_songs %>%
  specify(response = victory_win_won, explanatory = region, success = "Yes") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("north", "south"))

get_p_value(null_dist_north_south_victory, obs_stat = obs_diff_props_n_s_victory, direction = "two_sided")

visualise(null_dist_north_south_victory) + 
  labs(title = "Null Distribution for Difference in Proportions of Fight Songs that Include 'Victory', 'Win', or 'Won'",
       subtitle = "For Fight Songs that Include 'Victory', 'Win', or 'Won'",
       x = "Sample Difference in Proportions",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_props_n_s_victory, direction = "two_sided")
```

Based on our p-value of 0.418, which is greater than our significance level of 0.05, we fail to reject the null hypothesis. There is insufficient evidence that there is a difference in the proportion of fight songs that include "victory," "win," or "won" for southern and northern conferences.

Next, we will look at our second variable, `men`, which refers to whether a fight song mentions male groups in its lyrics, to see whether there exists a statistically significant relationship between the proportion of teams for which `men` is "yes" for northern or southern conferences.  First, we will find what the two proportions are:

```{r calc-prop-yes-men-n-s}
fight_songs %>%
  count(region, men) %>%
  group_by(region) %>%
  mutate(prop_men = n/sum(n))
```

Based on the output, 44.4% of schools in northern conferences mention male groups in their fight songs. On the other hand, only 31.6% of schools in southern conferences mention male groups in their fight songs. We would like to see if this result is statistically significant and what the true difference in proportions is. We have to use simulation-based hypothesis testing because we are looking for the difference in proportions.

First, we will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the proportion of fight songs that mention male groups for schools in northern vs. southern conferences. Our null hypothesis is that there is no difference in the proportion of schools that mention men in their fight songs for southern and northern conferences, H0: p(southern) = p(northern). Our alternative hypothesis is that there is a difference in the proportion of schools that mention men in their fight songs for southern and northern conferences, Ha: p(southern) ≠ p(northern). We will use a significance level of 0.05.

```{r hyp-test-men}
obs_diff_props_n_s_men <- 0.4444444	- 0.3157895 # From above code chunk

set.seed(11101962)
null_dist_north_south_men <- fight_songs %>%
  specify(response = men, explanatory = region, success = "Yes") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("north", "south"))

get_p_value(null_dist_north_south_men, obs_stat = obs_diff_props_n_s_men, direction = "two_sided")

visualise(null_dist_north_south_men) + 
  labs(title = "Null Distribution for Difference in Proportions",
       subtitle = "For Fight Songs that Mention Male Groups (N-S)",
       x = "Sample Difference in Proportions",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_props_n_s_men, direction = "two_sided")
```

Based on our p-value of 0.454, which is greater than our significance level of 0.05, we fail to reject the null hypothesis. There is insufficient evidence that there is a difference in the proportion of fight songs that mention male groups for southern and northern conferences.

Finally, we will look at our last variable, `nonsense`, which refers to whether a fight song uses nonsense syllables in its lyrics, to see whether there exists a statistically significant relationship between the proportion of teams for which `nonsense` is "yes" for northern or southern conferences.  First, we will find what the two proportions are:

```{r calc-prop-yes-nonsense-n-s}
fight_songs %>%
  count(region, nonsense) %>%
  group_by(region) %>%
  mutate(prop_nonsense = n/sum(n))
```

Based on the output, 14.8% of schools in northern conferences use nonsense syllables in their fight songs. On the other hand, 15.8% of schools in southern conferences use nonsense syllables in their fight songs. We would like to see if this result is statistically significant and what the true difference in proportions is. We have to use simulation-based hypothesis testing because we are looking for the difference in proportions.

First, we will run a hypothesis test, calculate the p-value, and interpret the results in order to determine whether there is a statistically significant difference in the proportion of fight songs that use nonsense syllables for schools in northern vs. southern conferences. Our null hypothesis is that there is no difference in the proportion of schools that use nonsense syllables in their fight songs for southern and northern conferences, H0: p(southern) = p(northern). Our alternative hypothesis is that there is a difference in the proportion of schools that mention men in their fight songs for southern and northern conferences, Ha: p(southern) ≠ p(northern). We will use a significance level of 0.05.

```{r hyp-test-nonsense}
obs_diff_props_n_s_nonsense <- 0.1481481	- 0.1578947 # From above code chunk

set.seed(11101962)
null_dist_north_south_nonsense <- fight_songs %>%
  specify(response = nonsense, explanatory = region, success = "Yes") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("north", "south"))

get_p_value(null_dist_north_south_nonsense, obs_stat = obs_diff_props_n_s_nonsense, direction = "both")

visualise(null_dist_north_south_nonsense) + 
  labs(title = "Null Distribution for Difference in Proportions",
       subtitle = "For Fight Songs with Nonsense Syllables (N-S)",
       x = "Sample Difference in Proportions",
       y = "Count") +
  shade_p_value(obs_stat = obs_diff_props_n_s_nonsense, direction = "two_sided")
```

Based on our p-value of 0.648, which is greater than our significance level of 0.05, we fail to reject the null hypothesis. There is insufficient evidence that there is a difference in the proportion of fight songs that use nonsense syllables for southern and northern conferences.

### Conclusion from Additional Analysis

We hypothesized that characteristics of fight songs would very depending on whether a fight song is from a team in a southern vs. northern athletic conference. We decided to look at the variables `victory_win_won`, `men`, and `nonsense` because we thought that out of all of the variables in our data set that these three might vary based on geographical location. 

However, based on the hypothesis testing above, it turns out that the variables `victory_win_won` (p = 0.418), `men` (p = 0.454), and `nonsense` (p = 0.648) are NOT regionally unique.  In other words, knowing whether a school is in a southern vs. northern conference does not tell us whether that school's fight song is more or less likely to include the words "victory", "win", or "won", mention male individuals/groups, or use nonsense words/phrases. The data leads us to believe that college fight songs are truly independent and random from one another.
